Timeliness of security updates for Android

### 2014-11-13 security_scoring.tex
Add manually annotated full_version_Comp diagram

\daTabSecScoresmodel
Even within device manufacturers different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \emph{\daSecScoreBestmodel} (\daSecScoreBestmodelScore\ out of 10) scoring highest and \emph{\daSecScoreWorstmodel} (\daSecScoreWorstmodelScore\ out of 10) scoring lowest.
We can then test whether this seems fair by comparing the version data for the highest and lowest scoring models.
Figure~\ref{fig:worst_model_full} shows the full version distribution for \emph{\daSecScoreWorstmodel} and Figure~\ref{fig:best_model_full} shows the same for \emph{\daSecScoreBestmodel}.
There is a marked difference in the distribution of updates between the two with only \daSecScoreWorstmodelNumFullVersions\ full versions for \emph{\daSecScoreWorstmodel} and \daSecScoreBestmodelNumFullVersions\ for \emph{\daSecScoreBestmodel}.

\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/full_version_\daSecScoreBestmodel.pdf}
  \caption{\daSecScoreBestmodel}
  \label{fig:best_model_full}
 \end{subfigure}
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/full_version_\daSecScoreWorstmodel.pdf}
  \caption{\daSecScoreWorstmodel}
  \label{fig:worst_model_full}
 \end{subfigure}
 \caption{Full version distributions for the highest and lowest scoring model}
\end{figure}

>>>>

\daTabSecScoresmodel
Even within device manufacturers different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \emph{\daSecScoreBestmodel} (\daSecScoreBestmodelScore\ out of 10) scoring highest and \emph{\daSecScoreWorstmodel} (\daSecScoreWorstmodelScore\ out of 10) scoring lowest.
We can then test whether this seems fair by comparing the version data for the highest and lowest scoring models.
Figure~\ref{fig:full_version_comp}b shows the full version distribution for \emph{\daSecScoreWorstmodel} and Figure~\ref{fig:full_version_comp}a shows the same for \emph{\daSecScoreBestmodel}.
There is a marked difference in the distribution of updates between the two with only \daSecScoreWorstmodelNumFullVersions\ full versions for \emph{\daSecScoreWorstmodel} and \daSecScoreBestmodelNumFullVersions\ for \emph{\daSecScoreBestmodel}.
Both device models start off with the full version string of `2.3.3 GRI40' but the \emph{\daSecScoreBestmodel} receives many more updates over the same time period.
Other models from the same manufacturer with similar model names to \emph{\daSecScoreWorstmodel} do much better such as the \emph{Desire HD}.

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/full_version_comp.pdf}
 \caption{Full version distributions for the highest and lowest scoring model}
 \label{fig:full_version_comp}
\end{figure}
